Plots for \enquote{Arrows for Parallel Computations}

### 2018-01-03 paper/separate_plots/main.tex
minor

\section{Plots}

@@

\newcommand{\meanOverheadPlot}[5]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
scale only axis, width=\plotwidthDist,
xlabel=Threads,
%xtick=data,
ytick distance=#2 / 4,
xtick distance=#3,
minor tick num=9,
ylabel=Overhead (\%),
ylabel near ticks,
grid=both,
legend entries={Mean Overhead},
legend style={at={(0.99,0.99)},anchor=north east},
max space between ticks=50pt,
grid style={line width=.1pt, draw=gray!10},
major grid style={line width=.2pt,draw=gray!50},
ymin=-#2,
ymax=#2,
xmin=-1,
xmax=#4]
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="overhead", y error="stdDevForOverhead", col sep=comma, mark=dots,
smooth]{#5};
\end{axis}
\end{tikzpicture}
}

@@

\subsection{Distributed}

\subsubsection{\rmtest}

\paragraph{Overhead}~\\

@@

\paragraph{Speedup}~\\

@@

\subsubsection{\jacobitest}

\paragraph{Overhead}~\\

@@

\subsubsection{\torustest}

@@

\subsection{Shared-Memory}

\subsubsection{\rmtest}

\paragraph{Speedup}~\\

@@

\paragraph{Overhead}~\\

@@

\subsubsection{\sudokutest}

\paragraph{Speedup}~\\

@@

\subsubsection{\torustest}

\paragraph{Speedup}~\\

@@

\paragraph{Overhead}~\\

\meanOverheadPlot{Mean Overhead for shared-memory \\ \torustest 512 vs Eden CP}{0.05}{4}{18}{\benchmarkDir/torus-sm/eden-cp-512-diff.csv}

>>>>

@@

\newcommand{\meanOverheadPlot}[5]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
scale only axis, width=\plotwidthDist,
xlabel=Threads,
%xtick=data,
ytick distance=#2 / 4,
xtick distance=#3,
minor tick num=9,
ylabel=Overhead,
ylabel near ticks,
grid=both,
legend entries={Mean Overhead},
legend style={at={(0.99,0.99)},anchor=north east},
max space between ticks=50pt,
grid style={line width=.1pt, draw=gray!10},
major grid style={line width=.2pt,draw=gray!50},
ymin=-#2,
ymax=#2,
xmin=-1,
xmax=#4]
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="overhead", y error="stdDevForOverhead", col sep=comma, mark=dots,
smooth]{#5};
\end{axis}
\end{tikzpicture}
}

@@

\section{Distributed Plots}

\subsection{\rmtest}

\subsubsection{Overhead}~\\

@@

\subsubsection{Speedup}~\\

@@

\subsection{\jacobitest}

\subsubsection{Overhead}~\\

@@

\subsection{\torustest}

@@

\section{Shared-Memory Plots}

\subsection{\rmtest}

\subsubsection{Speedup}~\\

@@

\subsubsection{Overhead}~\\

@@

\subsection{\sudokutest}

\subsubsection{Speedup}~\\

@@

\subsection{\torustest}

\subsubsection{Speedup}~\\

@@

\subsubsection{Overhead}~\\

\meanOverheadPlot{Mean Overhead for shared-memory \\ \torustest 512 vs Eden CP}{0.08}{4}{18}{\benchmarkDir/torus-sm/eden-cp-512-diff.csv}
